Viscous Erosion in Porous Media

### 2018-03-06 docs/methods/erosion_methods.tex
NM

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.9 \textwidth]{./figs/area_drag.pdf}
\caption{The area and drag of an eroding body: (a) The body area measured in the simulations (black) shown against the scaling-law prediction \eqref{area_predict} (dotted red). The two are nearly indistinguishable. (b) The horizontal drag (black) on the body as it erodes, along with the viscous (green) and pressure (blue) contributions. The scaling prediction can be rearranged to give estimate \eqref{viscdrag} for the viscous drag (dotted red).}
\label{area_drag}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure from datafile 01circ1024aaa;
% Uses 01circ1024.in with epsfac = 10, sigfac = 10, dt = 1e-7, fixarea = 0, fixpdrop = 0

@@

As a final check, we can estimate the drag (per unit span) using slender-body theory via the formula
\begin{align}
F_D \sim \frac{4 \pi \mu U}{\log(\ell/a)}
\end{align}
For a circular cylinder, $a$ is the radius and the prefactor $4 \pi$ above gives an exact result within the slender-body framework. To generalize to other shapes, we define $a = \sqrt{A/\pi}$ and fit $\ell$ to get $\ell = 2.3 a_0$.

>>>>

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.9 \textwidth]{./figs/area_drag.pdf}
\caption{The area and drag of an eroding body: (a) The body area measured in the simulations (black) shown against the scaling-law prediction \eqref{area_predict} (dotted red). The two are nearly indistinguishable. (b) The horizontal drag (black) on the body as it erodes, along with the viscous (green) and pressure (blue) contributions. The scaling prediction can be rearranged to give estimate \eqref{dragscaling} for the viscous drag (dotted red).}
\label{area_drag}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure from datafile 01circ1024aaa;
% Uses 01circ1024.in with epsfac = 10, sigfac = 10, dt = 1e-7, fixarea = 0, fixpdrop = 0

@@

As a final check, we can estimate the drag (per unit span) using slender-body theory via the formula
\begin{align}
\label{dragscaling}
\frac{F_D}{4 \pi} \sim \frac{ \mu U}{\log(\ell/a)}
\end{align}
For a {\em circular} cylinder, $a$ is the radius and the normalization factor $4 \pi$ is exact within the slender-body framework. To generalize to other shapes, we define $a = \sqrt{A/\pi}$ and fit $\ell$ to get $\ell = 2.3 a_0$.
